Updated Project Plan

### 2021-10-25 tex/Plan/Plan.tex
updated project plan - weekly.

>>>>

\begin{enumerate}[leftmargin=*]
	\item \textbf{!8th October 2021 -- 31st October 2021}\\
	Finish first paper
	\item \textbf{1st November 2021 -- 7th November 2021}\\
	Start on research for stochastic/exact method
	\item \textbf{8th November 2021 -- 14th November 2021}\\
	Continue research for stochastic/exact method
	\item \textbf{15th November 2021 -- 21st November 2021}\\
	Mee with Abicare for analysis of solutions, prep DST for release, finish documentation
	\item \textbf{22nd November 2021 -- 28th November 2021}
	Release DST and documentation, give DST to Abicare, send questionnaire
	\item \textbf{29th November 2021 -- 5th December 2021}
	Research for stochastic/exact method
	\item \textbf{6th December 2021 -- 12th December 2021}
	Research for stochastic/exact method
	\item \textbf{13th December 2021 -- 19th December 2021}
	Research for stochastic/exact method
	\item \textbf{20th December 2021 -- 26th December 2021}
	Start creating model for stochastic/exact method
	\item \textbf{3rd January 2022 -- 9th December 2022}
	Check and begin to implement model for stochastic/exact method
	\item \textbf{10th January 2022 -- 16th January 2022}
	Implement model into DST, debug
	\item \textbf{17th January 2022 -- 23rd January 2022}
	Start gathering data/creating instances to test model in DST
	\item \textbf{24th January 2022 -- 30th January 2022}
	Start testing model in DST
	\item \textbf{31st January 2022 -- 6th February 2022}
	Analyse data, begin paper
	\item \textbf{7th February 2022 -- 13th February 2022}
	Papers
	\item \textbf{14th February 2022 -- 20th February 2022}
	Papers
	\item \textbf{21st February 2022 -- 27th February 2022}
	Papers
	\item \textbf{28th February 2022 -- 6th March 2022}
	Papers
	\item \textbf{7th March 2022 -- 13th March 2022}
	Gather results from Abicare, compare, send another questionnaire
	\item \textbf{14th March 2022 -- 20th March 2022}
	Papers
	\item \textbf{21st March 2022 -- 27th March 2022}
	Papers
	\item \textbf{28th March 2022 -- 3rd April 2022}
	Papers
	\item \textbf{4th April 2022 -- 10th April 2022}
	Papers
	\item \textbf{11th April 2022 -- 17th April 2022}
	Papers
	\item \textbf{18th April 2022 -- 24th April 2022}
	Papers
	\item \textbf{25th April 2022 -- 30th April 2022}
	Conclude project.

\end{enumerate}
